Trait pleiotropy of regulatory variants increases with the variety of bound transcription factors, regulated genes and active tissues

### 2022-08-29 ms/ms03_results.tex
ENH ms and refactoring
ENH ms

I developed a colocalization pipeline that explored all the 51 625 combinations of eQTL studies and GWAS (Section Methods).
%
This analysis explored 30 261 unique variants and 2,479,065 potential variant colocalizations (OSF URL).
%
Selection of colocalizations with PP.H4.abf greater than 0.8 resulted in 9 758 variants and 143 119 colocalizations (Supplementary table 3).

@@

\subsection*{How do effect size and }

@@

In summary, I observed opposite effects of pleiotropy on the eQTL and GWAS variant strengths.

>>>>

I developed a colocalization pipeline that explored all the 51 625 combinations of eQTL studies and GWAS (Section Methods).
%
This analysis resulted in 30 261 unique variants and 2,479,065 potential variant colocalizations from 150 GWAS studies (OSF URL).
%
%TODO add PMID to supplementary table with loci_explained_perc
For GWAS studies with more than 10 loci, the explained of loci variate from 0\% to 77\% with an average of 33\% (Supplementary table ST6).
%
Autoimmune diseases such as inflammatory bowel disease, Crohn's disease and Ulcerative colitis showed a colocalization average of 45.4\% in agreement with previous work \citep{2021.Li.Mu.GenomeBiology.impactcelltype}.
%
Selection of colocalizations with PP.H4.abf greater than 0.8 resulted in 9 758 variants and 143 119 colocalizations (Supplementary table 3).

@@

\subsection*{How do effect size and significance relate to pleiotropy}

@@

### 2022-08-29 ms/ms04_discussion.tex
ENH ms

My colocalization pipeline was initially based on another pipeline that is at the eQTL Catalogue Github repository ( \url{https://github.com/eQTL-Catalogue/colocalisation} ).
%
First lead eQTLs with FDR 0.05 in each sample are selected and surrounding eQTL and GWAS variants with radius of 500,000 nt (Total window 1,000,000 nt) are retrieved.
%
Colocalization between eQTL and GWAS variants is tested using the "coloc.abf" function of CRAN coloc for each window, each eQTL sample and each GWAS.

>>>>

My colocalization pipeline was inspired by another pipeline that is at the eQTL Catalogue Github repository ( \url{https://github.com/eQTL-Catalogue/colocalisation} ).
%
GWAS were downloaded from OpenGWAS and converted to hg38 coordinates.
%
Permuted eQTLs with FDR 0.05 in each sample were selected as lead variants.
%
eQTL and GWAS variants surrounded the lead variants with radius of 500,000 nt (Total window 1,000,000 nt) were retrieved.
%
These variants were kept if MAF was strictly greater than 0 and lower than 1, the variants were not duplicated and there was no missing data.
%
Colocalization between eQTL and GWAS variants was tested using the "coloc.abf" function of CRAN coloc for each window, each eQTL sample and each GWAS.
